---
title: "Ex6.1"
author: "Guanting Wei"
date: "Oct.17.2018"
output: pdf_document
header-includes: 
  \usepackage{algorithm}
  \usepackage{algpseudocode}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Find function g
We have
$$g(x)\propto (2x^{\theta-1}+x^{\theta-\frac{1}{2}})e^{-x}$$
So
$$g(x)=C(2x^{\theta-1}+x^{\theta-\frac{1}{2}})e^{-x}$$
Because g is a mixture of gamma distribution, let's consider gamma distribution. 
$$f(x,\beta,\alpha)=\frac{\beta^\alpha}{\Gamma (\alpha)}x^{\alpha-1}e^{-\beta x}$$
According the formation of function g, we let $\beta=1$, $\alpha=\theta\ \ and\ \ \theta+\frac{1}{2}$. The component distributions are as follow.
$$f(x,1,\theta)=\frac{1}{\Gamma (\theta)}x^{\theta-1}e^{-x}$$
$$f(x,1,\theta+\frac{1}{2})=\frac{1}{\Gamma (\theta+\frac{1}{2})}x^{\theta-\frac{1}{2}}e^{-x}$$
Due to the Properties of density functions, we have 
$$\int_{-\infty}^{\infty}f(x)\mathrm{d}x=1$$
\[
\begin{aligned}
&\int_{-\infty}^{\infty}f(x,1,\theta)\mathrm{d}x=\int_{0}^{\infty}\frac{1}{\Gamma (\theta)}x^{\theta-1}e^{-x}\mathrm{d}x=1\\
&\int_{-\infty}^{\infty}f(x,1,\theta+\frac{1}{2})\mathrm{d}x=\int_{0}^{\infty}\frac{1}{\Gamma (\theta+\frac{1}{2})}x^{\theta-\frac{1}{2}}e^{-x}\mathrm{d}x=1\\
&\int_{0}^{\infty}x^{\theta-1}e^{-x}\mathrm{d}x=\Gamma (\theta)\\
&\int_{0}^{\infty}x^{\theta-\frac{1}{2}}e^{-x}\mathrm{d}x=\Gamma (\theta+\frac{1}{2})
\end{aligned}
\]
\[
\begin{aligned}
\int_{0}^{\infty}g(x)\mathrm{d}x&=C\int_{0}^{\infty}(2x^{\theta-1}+x^{\theta-\frac{1}{2}})e^{-x}\mathrm{d}x\\&=C[\int_{0}^{\infty}2x^{\theta-1}e^{-x}\mathrm{d}x+\int_{0}^{\infty}x^{\theta-\frac{1}{2}}e^{-x}\mathrm{d}x]\\&=C[2\Gamma (\theta)+\Gamma (\theta+\frac{1}{2})]=1\\
&\Rightarrow C=\frac{1}{2\Gamma (\theta)+\Gamma (\theta+\frac{1}{2})}
\end{aligned}
\]
So
$$g(x)=\frac{2\Gamma (\theta)}{2\Gamma (\theta)+\Gamma(\theta+\frac{1}{2})}\frac{x^{\theta-1}e^{-x}}{\Gamma (\theta)}+\frac{\Gamma(\theta+\frac{1}{2})}{2\Gamma (\theta)+\Gamma(\theta+\frac{1}{2})}\frac{x^{\theta-\frac{1}{2}}e^{-x}}{\Gamma(\theta+\frac{1}{2})}$$
Weights are $\frac{2\Gamma (\theta)}{2\Gamma (\theta)+\Gamma(\theta+\frac{1}{2})}$ for $f(x,1,\theta)$ and $\frac{\Gamma(\theta+\frac{1}{2})}{2\Gamma (\theta)+\Gamma(\theta+\frac{1}{2})}$ for $f(x,1,\theta+\frac{1}{2})$

# 2. Sample
## 2.1 Pseudo-code 

\begin{algorithm}
\begin{algorithmic}[1]
\Procedure{}{}
\State $P\sim U(0, 1)$
\If{$P < \frac{2\Gamma(\theta)}{2\Gamma(\theta)+\Gamma(\theta+\frac{1}{2})}$}
\State $X\sim (\theta, 1)$
\Else
\State $X\sim (\theta+\frac{1}{2}, 1)$
\EndIf
\State\Return $X$
\EndProcedure
\end{algorithmic}
\caption{Sampling from $g(x)$}
\end{algorithm}

## 2.2 Code
```{r}
library(abind)
g=function(x,theta){
  (2*x^(theta-1)+x^(theta-0.5))*exp(-x)/(2*gamma(theta)+gamma(theta+0.5))
}

sample_g=function(n,alpha,beta,weight){
  x_g=array(0,n)
  p1=runif(n,0,1)
  f1=rgamma(n,alpha[1],beta[1])
  f2=rgamma(n,alpha[2],beta[2])
  x_g=abind(f1[p1<weight],f2[p1>=weight])
}
n=10000
theta=1
alpha=c(theta,theta+0.5)
beta=c(1,1)
weight=2*gamma(theta)/(2*gamma(theta)+gamma(theta+0.5))
x=sample_g(n,alpha,beta,weight)
library(ggplot2)
ggplot(data.frame(x=x),aes(x=x))+
  xlab("x")+
  ylab("density")+
  ggtitle("Gamma mixture distribution")+
  geom_histogram(aes(y=..density..),fill="gray", colour="black")+
  geom_density(fill="green",colour="green" ,alpha=0.2)+
  stat_function(fun=function(x) g(x,theta),color="red")+
  annotate("text", x=9, y=0.6, label="Kernel",color="green")+
  annotate("text", x=9, y=0.5, label="True",color="red")
```

# 3. Rejection Sampling
$$f(x)\propto h(x)=\sqrt{x+4}x^{\theta-1}e^{-x}$$
$$E=\int_{0}^{\infty}h(x)\mathrm{d}x=\int_{0}^{\infty}\sqrt{x+4}x^{\theta-1}e^{-x}\mathrm{d}x$$
$$f(x)=\frac{h(x)}{E}$$
$$f(x)\leq Mg(x)\\
\Rightarrow M=max(\frac{f(x)}{g(x)})$$
$$\frac{f(x)}{g(x)}=\frac{\sqrt{x+4}x^{\theta-1}e^{-x}}{CE(2x^{\theta-1}+x^{\theta-\frac{1}{2}})e^{-x}}=\frac{\sqrt{x+4}}{CE(2+\sqrt{x})}$$
In order to calculate $max(\frac{f(x)}{g(x)})$, let $q(x)=\frac{f(x)}{g(x)}=\frac{\sqrt{x+4}}{CE(2+\sqrt{x})}$
$$q'(x)=\frac{1}{CE}\frac{\frac{1}{2\sqrt{x+4}}(2+\sqrt x)-\frac{1}{2\sqrt x}\sqrt{x+4}}{(2+\sqrt x)^2}
=\frac{1}{CE}\frac{2\sqrt x-4}{2\sqrt{x+4}\sqrt x(2+\sqrt x)^2}$$
We can know that when $x<4$,$q'(x)<0$;when $x>4$,$q'(x)>0$. So max(q(x)) can be q(0) or q($\infty$). $q(0)=\frac{1}{CE}=q(\infty)$. $$M=max(\frac{f(x)}{g(x)})=\frac{1}{CE}$$

$\\$

## 3.1 Pseudo-code 


\begin{algorithm}
\begin{algorithmic}[1]
\Procedure{}{}
\State Sample $P\sim U(0, 1)$
\If{$P\leq\frac{f(x)}{Mg(x)}=\frac{\sqrt{x+4}}{(2+\sqrt{x})}$}
\State\Return X
\Else
\State go back to 2
\EndIf
\EndProcedure
\end{algorithmic}
\caption{Sampling from $f(x)$}
\end{algorithm}

## 3.2 Code

```{r}
sample_f=function(n,alpha,beta,weight){
  x_f=rep(0,n)
  count=1
  while(count<=n){
  x_g=sample_g(1,alpha,beta,weight)
  p2=runif(1,0,1)
  if(p2<=sqrt(x_g+4)/(2+sqrt(x_g))){
    x_f[count]=x_g
    count=count+1
  }
  }
  x_f
}

h=function(x,theta){
  sqrt(x+4)*x^(theta-1)*exp(-x)
}

f=function(x,theta){
  h(x,theta)/integrate(function(x)h(x,theta),0,Inf)$value
}

n=10000
theta=1
alpha=c(theta,theta+0.5)
beta=c(1,1)
weight=2*gamma(theta)/(2*gamma(theta)+gamma(theta+0.5))
x_f=sample_f(n,alpha,beta,weight)
```


```{r}
ggplot(data.frame(x=x_f),aes(x=x))+
  xlab("x")+
  ylab("density")+
  ggtitle("distribution of f(x)")+
  geom_histogram(aes(y=..density..),fill="gray", colour="black")+
  geom_density(fill="green",colour="green" ,alpha=0.2)+
  stat_function(fun=function(x) g(x,theta),color="red")+
  annotate("text", x=7.5, y=0.5, label="Kernel",color="green")+
  annotate("text", x=7.5, y=0.4, label="True",color="red")
```


