---
title: "Ex6.2"
author: "Guanting Wei"
date: "Oct.17.2018"
output: pdf_document
header-includes: 
  \usepackage{algorithm}
  \usepackage{algpseudocode}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Define instrumental density
$$f(x)\propto h(x)=\frac{x^{\theta-1}}{1+x^2}+\sqrt{2+x^2}(1-x)^{\beta-1},x\in (0,1)$$
$$h(x)\leq q(x)=x^{\theta-1}+\sqrt{3}(1-x)^{\beta-1}$$
$$g_1(x)=g_1(x;\theta,1)=\frac{x^{\theta-1}}{B(\theta,1)}=\theta x^{\theta-1}$$
$$g_2(x)=g_2(x;1,\beta)=\frac{(1-x)^{\beta-1}}{B(1,\beta)}=\beta (1-x)^{\beta-1}$$
$$g(x)=Cq(x)=C(x^{\theta-1}+\sqrt{3}(1-x)^{\beta-1})=C(\frac{1}{\theta}\theta x^{\theta-1}+\frac{\sqrt{3}}{\beta}\beta (1-x)^{\beta-1})$$
$$C=\frac{\theta \beta}{\beta+\sqrt{3}\theta}$$
$$p_1=\frac{C}{\theta}=\frac{\beta}{\beta+\sqrt{3}\theta},p_2=\frac{C}{\beta}=\frac{\theta}{\beta+\sqrt{3}\theta}$$
Let $M=\frac{1}{C}$ $h(x)\leq Mg(x)=q(x)$

# 2. Sampling
## 2.1 Pseudo-code

\begin{algorithm}
\begin{algorithmic}[1]
\Procedure{}{}
\State $P\sim U(0, 1)$
\If{$P\leq p_1$}
\State $X\sim g_1(x)$
\Else
\State $X\sim g_2(x)$
\EndIf
\State $P'\sim U(0, 1)$
\If{$P'\leq \frac{h(x)}{Mg(x)}=\frac{h(x)}{q(x)}$}
\State\Return X
\Else
\State go back to 2
\EndIf
\EndProcedure
\end{algorithmic}
\caption{Sampling from $f(x)$}
\end{algorithm}

## 2.2Code
```{r}
library(abind)
sample_g=function(n,a,b,weight){
  x_g=rep(0,n)
  p1=runif(n,0,1)
  g1=rbeta(n,a[1],b[1])
  g2=rbeta(n,a[2],b[2])
  x_g=abind(g1[p1<=weight],g2[p1>weight])
  x_g
}

h=function(x,a,b){
  x^(a[1]-1)/(1+x^2)+sqrt(2+x^2)*(1-x)^(b[2]-1)
}

f=function(x,a,b){
  h(x,a,b)/integrate(function(x)h(x,a,b),0,1)$value
}

q=function(x,a,b){
  x^(a[1]-1)+sqrt(3)*(1-x)^(b[2]-1)
}

sample_f=function(n,a,b,weight){
  x_f=rep(0,n)
  count=1
  while(count<=n){
    x_g=sample_g(1,a,b,weight)
    p2=runif(1,0,1)
    if(p2<=h(x_g,a,b)/q(x_g,a,b)){
      x_f[count]=x_g
      count=count+1
    }
  }
  x_f
}
```
Let $(\theta,\beta)=(2,3)$
```{r}
n=10000
theta=2
beta=3
a=c(theta,1)
b=c(1,beta)
weight=beta/(beta+sqrt(3)*theta)
x=sample_f(n,a,b,weight)
library(ggplot2)
ggplot(data.frame(x=x),aes(x=x))+
  xlab("x")+
  ylab("density")+
  ggtitle("distribution of f(x)")+
  geom_histogram(aes(y=..density..),fill="gray", colour="black")+
  geom_density(fill="green",colour="green" ,alpha=0.2)+
  stat_function(fun=function(x) f(x,a,b),color="red")+
  annotate("text", x=0.6, y=1.5, label="Kernel",color="green")+
  annotate("text", x=0.6, y=1.4, label="True",color="red")
```

# 3. Dealing With the Two Components 
$$h_1(x)=\frac{x^{\theta-1}}{1+x^2}\ \ \ \ \ \ \ \ \ h_2(x)=\sqrt{2+x^2}(1-x)^{\beta-1}, x\in (0,1)$$
$$g_1(x)=\theta x^{\theta-1}\ \ \ \ \ \ \ \ \ g_2(x)=\beta (1-x)^{\beta-1}, x\in (0,1)$$
$$M_1=\frac{1}{\theta}\ \ \ \ \ \ \ \ \ M_2=\frac{\sqrt{3}}{\beta}$$
$$f(x)\propto h_1(x)+h_2(x)\\ $$
$$h_1(x)\leq M_1g_1(x)$$
$$ h_2(x)\leq M_2g_2(x)$$
$\\$

## 3.1 Pseudo-code
$\\$
\begin{algorithm}
\begin{algorithmic}[1]
\Procedure{}{}
\State $P\sim U(0, 1)$

\If{$P\leq \frac{M_1}{M_1+M_2}$}
\State $X\sim g_1(x)$ 
\State $P_1\sim U(0, 1)$
\If{$P_1\leq \frac{h_1(x)}{M_1g_1(x)}$}
\Return X
\Else go back to 2
\State $X\sim g_2(x)$
\EndIf

\Else
\State $X\sim g_2(x)$ 
\State $P_2\sim U(0, 1)$
\If{$P_2\leq \frac{h_2(x)}{M_2g_2(x)}$}
\Return X
\Else  
\State go back to 2
\EndIf

\EndIf
\EndProcedure
\end{algorithmic}
\caption{Sampling from $f(x)$}
\end{algorithm}
$\\$



## 3.2 Code
```{r}
h1=function(x,theta){
  x^(theta-1)/(1+x^2)
}
h2=function(x,beta){
  sqrt(2+x)*(1-x)^(beta-1)
}
g1=function(x,theta){
  theta*x^(theta-1)
}
g2=function(x,beta){
  beta*(1-x)^(beta-1)
}
f=function(x,a,b){
  h(x,a,b)/integrate(function(x)h(x,a,b),0,1)$value
}
sample_f=function(n,a,b){
  x_f=rep(0,n)
  M1=1/a[1]
  M2=sqrt(3)/b[2]
  weight=M1/(M1+M2)
  count=1
  while(count<=n){
    p=runif(1,0,1)
    if(p<=weight){
      x=rbeta(1,a[1],b[1])
      p1=runif(1,0,1)
      if(p1<=h1(x,a[1])/(M1*g1(x,a[1]))){
        x_f[count]=x
        count=count+1
      }
    }
    else{
      x=rbeta(1,a[2],b[2]) 
      p2=runif(1,0,1)
      if(p2<=h2(x,b[2])/(M1*g1(x,b[2]))){
        x_f[count]=x
        count=count+1
      }
    }
  }
  x_f
}
```

Let $\theta=2$,$\beta=3$, same as above.
```{r}
theta=2
beta=3
a=c(theta,1)
b=c(1,beta)
x=sample_f(n,a,b)
library(ggplot2)
ggplot(data.frame(x=x),aes(x=x))+
  xlab("x")+
  ylab("density")+
  ggtitle("distribution of f(x)")+
  geom_histogram(aes(y=..density..),fill="gray", colour="black")+
  geom_density(fill="green",colour="green" ,alpha=0.2)+
  stat_function(fun=function(x) f(x,a,b),color="red")+
  annotate("text", x=0.6, y=1.5, label="Kernel",color="green")+
  annotate("text", x=0.6, y=1.4, label="True",color="red")
```

